Supporting Information

### 2015-12-15 ms.Rmd
Added number of panicles to st_libStats

To investigate gene expression during the development of the rice inflorescence, laser microdissection (LMD) was used to collect meristematic tissues from the rachis meristem (RM), primary branch meristem (PBM), elongating primary branch meristem with axillary meristem (ePBM/AM) and spikelet meristem (SM) of early panicles (`r I(pasteLabel("Figure ", figCount, "f_lmdFigure"))`). RNA isolated from the meristem samples was amplified and used to produce cDNA libraries for sequencing. RNA input for amplification was between `r min(st_libStats$"Yield (ng)")` and `r max(st_libStats$"Yield (ng)")` ng and the average RNA integrity number (RIN) was `r round(mean(st_libStats$"RIN"), 1)` (`r I(pasteLabel("Table S", s_tableCount, "st_libStats"))`; **Number of panicles used for each library**). Initially, two biological replicates were prepared for each stage, but after performing a principal components analysis (PCA) on transformed expression values, two libraries that were produced from degraded RNA (RIN < 6.5) were excluded from the analysis (`r I(pasteLabel("Figure S", s_figCount, "sf_pca"))`). Following this, further samples were prepared to provide a total of three biological replicates with intact RNA (RIN ≥ 7) for each meristem type.

>>>>

To investigate gene expression during the development of the rice inflorescence, laser microdissection (LMD) was used to collect meristematic tissues from the rachis meristem (RM), primary branch meristem (PBM), elongating primary branch meristem with axillary meristem (ePBM/AM) and spikelet meristem (SM) of early panicles (`r I(pasteLabel("Figure ", figCount, "f_lmdFigure"))`). RNA isolated from the meristem samples was amplified and used to produce cDNA libraries for sequencing. RNA input for amplification was between `r min(st_libStats$"Yield (ng)")` and `r max(st_libStats$"Yield (ng)")` ng and the average RNA integrity number (RIN) was `r round(mean(st_libStats$"RIN"), 1)` (`r I(pasteLabel("Table S", s_tableCount, "st_libStats"))`). Initially, two biological replicates were prepared for each stage, but after performing a principal components analysis (PCA) on transformed expression values, two libraries that were produced from degraded RNA (RIN < 6.5) were excluded from the analysis (`r I(pasteLabel("Figure S", s_figCount, "sf_pca"))`). Following this, further samples were prepared to provide a total of three biological replicates with intact RNA (RIN ≥ 7) for each meristem type.

### 2015-12-15 si.Rmd
Added number of panicles to st_libStats

``` {r st_libstats, results = "asis"}
st_libStats_x <- as.data.frame(st_libStats)
rownames(st_libStats_x) <- st_libStats_x$Library
st_libStats_x$Library <- NULL
st_libStats_x$Sample <- sub("ePBM/SBM", "AM¹", st_libStats_x$Sample, fixed = TRUE)
st_libStats_x <- xtable::xtable(st_libStats_x)
xtable::align(st_libStats_x) <- rep("r", ncol(st_libStats_x) + 1)
xtable::digits(st_libStats_x) <- c(rep(0, 3), 3, rep(1, 11), 0)
st_libStats_x_print <- print(st_libStats_x,
      caption.placement = "top",
      comment = FALSE,
      rotate.colnames = TRUE,
      floating = TRUE,
      floating.environment = "table*",
      print.results = FALSE)

>>>>

``` {r st_libstats, results = "asis"}
st_libStats_x <- as.data.frame(st_libStats)
rownames(st_libStats_x) <- st_libStats_x$Library
st_libStats_x$Library <- NULL
st_libStats_x$Sample <- sub("ePBM/SBM", "AM¹", st_libStats_x$Sample, fixed = TRUE)
st_libStats_x <- xtable::xtable(st_libStats_x)
xtable::align(st_libStats_x) <- rep("r", ncol(st_libStats_x) + 1)
xtable::digits(st_libStats_x) <- c(rep(0, 4), 3, rep(1, 11), 0)
st_libStats_x_print <- print(st_libStats_x,
      caption.placement = "top",
      comment = FALSE,
      rotate.colnames = TRUE,
      floating = TRUE,
      floating.environment = "table*",
      print.results = FALSE)
